---
output: html_document
pagetitle: "Homework 2, Group 9: to the Client"
---

 ```{css, echo=FALSE}
     .disclosure{
     text-align: justify;
     margin-left: auto;
     margin-right: auto;
     font-style: italic;
     width: 80%;
     }

```

## Dear valued Client,
### Please find below our finalized report with your current options. Please contact us if you need anything else, we will be happy to assist you in this new journey!.
\

#### Best regards,
##### Ana Gabriela Itokazu, Jianfeng Zhang, and Takhellambam Bijoychandra Singh.

***
<div class="disclosure">

Portfolio developed for a homework activity during the class STAT 6210 - R Programming for Data Science (Auburn University, Fall 2020). The general idea is that the group works as a quantitative analysts for an investment bank, and we needed to present a Portfolio for our boss (Dr. Molinari, in this very real case) with a client's options. This document was produced in RMarkDown, and finalized in `r format(Sys.Date(), '%B %d, %Y')`. One can find more about this assignment [here](https://github.com/AU-R-Programming/HW2-9/blob/master/ToTheClient.Rmd).

</div>

***
<div style="text-align: justify">

# Financial Report

#### Required output: Produce a short html file (not more than the equivalent of two pages) representing a brief financial report for the client (no code details) describing what was done and what your conclusions are.

Suppose that you are working in an investment bank as a quantitative analyst. Your boss asks you to create a portfolio for one of your clients. The client wants to find the portfolio with the smallest variance that satisfies the following constraints:

- Considers only 5 companies of the S&P500.
- The investment C is exactly $1,000,000.
- You are allowed to invest in a maximum of 3 stocks.

If needed, it is possible to consider weights with negative values. This means that you are allowed to short stocks.

Your boss wants you to compute all possible portfolios that satisfy the client’s constraints, for each portfolio size (i.e. 1, 2 and 3 stocks) create a matrix with understandable row and column names in which, for each portfolio, you will store weights (when considering more than one stock in a portfolio),
expected returns and risk, represent them graphically as (for example) in the graph below, and provide the weights of the best (i.e. minimum variance) portfolio with expected return and risk (i.e. variance).
For the last task, in order to find the optimal weights we denote the vector of weights as \(\mathbf{w} \in \mathbb{R}^p\), where \(p\) is the number of stocks to invest, and denote the variance-covariance matrix of stocks as \(\mathbf{\Sigma}\). Then given the constraint that \(\mathbf{w}^T \mathbf{1} = 1\), where \(\mathbf{1}\) is the vector of \(1\) of length \(p\), we can construct the objective function with Lagrange multiplier as \(f(\mathbf{w}) = \mathbf{w}^T \mathbf{\Sigma} \mathbf{w} + \lambda(\mathbf{w}^T \mathbf{1} - 1)\) with some \(\lambda\). The optimal weights are therefore given by \[
\mathbf{w}^* = \frac{\mathbf{\Sigma}^{-1} \mathbf{1}}{\mathbf{1}^T \mathbf{\Sigma}^{-1} \mathbf{1}}.
\] Based on these weights, the expected return and risk are respectively given by \[\mu^* = ({\mathbf{w}^*}^T \mathbf{\mu}) \,C\] and \[\sigma^* = ({\mathbf{w}^*}^T \mathbf{\Sigma} \mathbf{w}^*) \, C^2\] where \(\mathbf{\mu}\) is the vector of expected (average) returns and \(C\) is the total investment.









</div>

# Required Library.

First of required libraries i.e. rvest, quantmod and tidyverse are called. 
```{r stock, echo=TRUE}
library(rvest)
library(quantmod)
library(tidyverse)
```

# Stock selection.



```{r stock1, echo=TRUE}
url <- "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"
SP500 <- url %>%
  xml2::read_html() %>%
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[1]') %>%
  html_table()
SP500 <- SP500[[1]]
Tix <- SP500$Symbol
#randomly select 5 stocks
set.seed(100)
s=sample(Tix, 5)
```
Five stocks were selected randomly that download from this [link](https://en.wikipedia.org/wiki/List_of_S%26P_500_companies) i.e. `r s` where 

`r s[1]`=fORTIVE Corp, `r s[2]`= Zimmer Biomet Holdings, `r s[3]`=Oracle Corp., `r s[4]`=Citrix Systems, and `r s[5]`=Xilinx.

# Temporal Scale 

In this analysis, a  time span for last 3 years i.e. from  "2017-04-01" till "2020-04-01" were considered.
```{r stock2, echo=TRUE}
#time span for last 3 years
three_year_ago <- seq(as.Date("2020-04-01"), length = 2, by = "-3 year")[2]
getSymbols(s, from = three_year_ago, to = as.Date("2020-04-01"))
```



# Compute returns

Here clcl() function is used to compute change in closing price.
For example, "AAPL" company has change in closing price( clcl) as given below
clcl= ((AAPL.Close at t+1 )-(AAPL.Close t))/(AAPL.Close at  t), where t= time step

```{r stock3, echo=TRUE}

FTV<- na.omit(ClCl(get(s[1])))
ZBH <- na.omit(ClCl(get(s[2])))
ORCL<- na.omit(ClCl(get(s[3])))
CTXS <- na.omit(ClCl(get(s[4])))
XLNX<- na.omit(ClCl(get(s[5])))
```

# Matrix 

 This first matrix has 10x7 dimensions as it considers 3 portfolio out of 5 giving a combination of C(5,3)=10 portfolios.
```{r stock4, echo=TRUE}
final=matrix(NA,10, 7)
colnames(final)=c(s,"Exp return","Risk")
```

The below code estimate weight,the daily expected return and risk considering  stocks out of 5 giving a combination of C(5,3)=10 portfolios.

```{r stock5, echo=TRUE}
for (i in 1:10) {
  # attributes the returns data to a new object
  stocks=cbind(FTV,ZBH,ORCL,CTXS,XLNX)
  #compute the combination of picking 3 stocks out of 5 eqXLNXs to 10
  mat <- combn(1:5, 3)
  #converts to a list  with each element consist of 3 stocks
  aa=split(mat, rep(1:ncol(mat), each = nrow(mat)))
  #select 3 stocks from the object stocks having 5 stocks
  x=stocks[,aa[[i]]] 
  # Estimation of mu and Sigma
  sigma_stocks <- cov(x)
  colnames(sigma_stocks)=c("Stock1","Stock2","Stock3")
  mu <-sapply(x, mean)
  # Compute weight
  p<-c(1,1,1)
  num <-solve(sigma_stocks)%*%p
  den=t(p) %*% solve(sigma_stocks)%*%p
  omega_star <-1/den[1] * num
  # C= total amount of investment i.e. 1 million
  C=1e6
  #computes the expected daily returns
  mu_star <-t(omega_star)%*% mu*C
  # computes the daily risk 
  sigma_star=t(omega_star)%*%sigma_stocks%*%omega_star*C^2
  #Insert the expected daily return to the predefined matrix
  final[i,aa[[i]]]=c(t(omega_star))
   #Insert the daily risk to the predefined matrix
  final[i,6:7]=c(mu_star,sigma_star)
}
#replace all NA value with 0
# this is the final output showing weight, daily return and risk for considering 3 stocks out of 5.
stock3=replace_na(final,0)
```

Likewise, this loop will estimate weight,the daily expected return and risk considering 2 stocks out of 5 giving a combination of C(5,2)=10 portfolios. The procedure is indeed same as done above code.

```{r stock6, echo=TRUE}
# Selecting stock2
final1=matrix(NA,10, 7)
colnames(final)=c(s,"Exp return","Risk")
for (i in 1:10) {
  stocks=cbind(FTV,ZBH,ORCL,CTXS,XLNX)
  mat <- combn(1:5, 2)
  aa=split(mat, rep(1:ncol(mat), each = nrow(mat)))
  x=stocks[,aa[[i]]] 
  sigma_stocks <- cov(x)
  colnames(sigma_stocks)=c("Stock1","Stock2")
  mu <-sapply(x, mean)
  p<-c(1,1)
  num <-solve(sigma_stocks)%*%p
  den=t(p) %*% solve(sigma_stocks)%*%p
  omega_star <-1/den[1] * num
  C=1e6
  mu_star <-t(omega_star)%*% mu*C
  sigma_star=t(omega_star)%*%sigma_stocks%*%omega_star*C^2
  final1[i,aa[[i]]]=c(t(omega_star))
  final1[i,6:7]=c(mu_star,sigma_star)
}
stock2=replace_na(final1,0)
```

Again, this loop will estimate weight, the daily expected return and risk considering 1 stocks out of 5 giving a combination of C(5,1)=5 is available. The procedure is indeed same as done above code.

```{r stock7, echo=TRUE}
final2=matrix(NA,5, 7)
colnames(final)=c(s,"Exp return","Risk")
for (i in 1:5) {
  stocks=cbind(FTV,ZBH,ORCL,CTXS,XLNX)
  mat <- combn(1:5, 1)
  aa=split(mat, rep(1:ncol(mat), each = nrow(mat)))
  x=stocks[,aa[[i]]] 
  sigma_stocks <- cov(x)
  mu <-sapply(x, mean)
  p<-c(1)
  num <-solve(sigma_stocks)%*%p
  den=t(p) %*% solve(sigma_stocks)%*%p
  omega_star <-1/den[1] * num
  C=1e6
  mu_star <-t(omega_star)%*% mu*C
  sigma_star=t(omega_star)%*%sigma_stocks%*%omega_star*C^2
  final2[i,aa[[i]]]=c(t(omega_star))
  final2[i,6:7]=c(mu_star,sigma_star)
}
stock1=replace_na(final2,0)
```
 
 Here, *stock* matrix showed the combine portfolios showing  with using stock size of 3,2 and 1 having a total of 25 portfolios.

```{r stock8, echo=TRUE}
#combing all portfolios
stock=rbind(stock3,stock2,stock1)
#showing output
stock
```

The best portfolios with its weight of stocks, daily expected return as well as risk is provided.
```{r stock9, echo=TRUE}
#choose the row showing minimum risk
min_risk=which.min(stock[,7])
# rounding the values upto 5 decimals
best=round(stock[min_risk,],5)
best
```

Graphically, it is shown in the plot below. The red dotted showed best portfolio out of the 25 portfolios shown in black having minimum risk of `r best[7]` and daily expected return of `r best[6]`. The weight for each stocks of *FTV*, *ZBH*, and *CTXS* are `r best[1]`,`r best[2]`, and `r best[4]` respectively. So, the portfolio 2 is the best option one can invest considering the minimum risk.
```{r stock10, echo=TRUE}
#plot of all portfolios
plot(stock[-min_risk,7],stock[-min_risk,6],pch=1,type = "p",  col = 1, 
     xlab = "Investment Daily Risk",
     ylab = "Investment Daily Expected Return", main="Stock Portfolios")
#addition of portfolio having smallest variance
points(best[7], best[6],pch = 1, col = 10, type = "p")
#add legends
legend(5.8e8,1500, c("Possible portfolio", "Min-Variance Portfolio"), col = c(1,10),
       lty = c(-2, -1), pch = c(1, 1))

```


