---
output: html_document
pagetitle: "Homework 2, Group 9: to the Boss"
---

 ```{css, echo=FALSE}
     .disclosure{
     text-align: justify;
     margin-left: auto;
     margin-right: auto;
     font-style: italic;
     width: 80%;
     }

```



***

<div class="disclosure">

Report developed for a homework activity during the class STAT 6210 - R Programming for Data Science (Auburn University, Fall 2020). The general idea is that the group works as a quantitative analysts for an investment bank, and we needed to present a Portfolio for our boss (Dr. Molinari, in this very real case) with the a client's options. This document was finalized in `r format(Sys.Date(), '%B %d, %Y')`. One can find more about this assignment [here](https://github.com/AU-R-Programming/HW2-9/blob/master/ToTheBoss.Rmd).

</div>

***

***


## Dear Boss,
### Please find our finalized report below.

\

#### Best regards,
##### Ana Gabriela Itokazu, Jianfeng Zhang, and Takhellambam Bijoychandra Singh.


***

<div style="text-align: justify">

\

# Financial Report

The team generated 25 portfolios options for the Client, based on their specified constraints, such as:

- Only 5 companies of S&P 500 were considered.
- The Client's investment is $1,000,000.
- The maximum portfolio size is 3 stocks.

To do that, specific libraries (*i.e.* `rvest`, `quantmod`, `tidyverse`, `knitr`, and `plotly`) are used in an `R` Programming Environment. 
</div>

```{r libraries, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
library(rvest)
library(quantmod)
library(tidyverse)
library(plotly) 
library(knitr)
```

\

<div style="text-align: justify">

### Stock selection

Five stocks were selected from [S&P 500](https://en.wikipedia.org/wiki/List_of_S%26P_500_companies) randomly:

</div>

```{r random_sample, echo=TRUE, warning=FALSE}
url <- "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"
SP500 <- url %>%
  xml2::read_html() %>%
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[1]') %>%
  html_table()
SP500 <- SP500[[1]]
# gets full list of stocks in SP500
Tix <- SP500$Symbol

# makes the code reproducible and samples randomly 5 stocks from SP500
set.seed(100) 
stocks_names <- sample(Tix, 5)
```


<div style="text-align: justify">

The stocks selected are:

- Fortive Corp (`r stocks_names[1]`)
- Zimmer Biomet Holdings Inc. (`r stocks_names[2]`)
- Oracle Corporation (`r stocks_names[3]`)
- Citrix Systems, Inc. (`r stocks_names[4]`)
- Xilinx, Inc. (`r stocks_names[5]`)

\

### Data time frame for Analysis 

In this analysis, a time span for the last 3 years (*i.e.* from  "2017-09-01" to "2020-09-01") was considered, and the data was fetched from the S&P 500 data base:

</div>

```{r time_fetch, echo=TRUE, warning=FALSE, message=FALSE}
#time span for last 3 years
three_year_ago <- seq(as.Date("2020-04-01"), length = 2, by = "-3 year")[2]
#fetch data from web
getSymbols(stocks_names, from = three_year_ago, to = as.Date("2020-04-01"))
```

\


<div style="text-align: justify">

### Compute returns

To compute the change in closing price values for each stock, the `ClCl()` function was applied to each of the stock's data, and all stocks were combined into one `xts` object:

</div>

```{r ClCl, echo=TRUE, warning=FALSE}

FTV <- na.omit(ClCl(get(stocks_names[1]))) # Fortive Corp
ZBH <- na.omit(ClCl(get(stocks_names[2]))) # Zimmer Biomet Holdings Inc.
ORCL <- na.omit(ClCl(get(stocks_names[3]))) # Oracle Corporation
CTXS <- na.omit(ClCl(get(stocks_names[4]))) # Citrix Systems, Inc.
XLNX <- na.omit(ClCl(get(stocks_names[5]))) # Xilinx, Inc.

stocks_considered <- cbind(FTV, ZBH, ORCL, CTXS, XLNX)
colnames(stocks_considered) = c("FTV", "ZBH", "ORCL", "CTXS", "XLNX")

```

\

<div style="text-align: justify">

### Matrix 

Then we proceed to generate portfolio options for the client, with portfolio sizes of 1, 2, and 3 stocks, computing the respective expected returns and risk for each portfolio, and providing the weights of the stocks in each portfolio option:

</div>

```{r prepping_loop, echo=TRUE, warning=FALSE}
# assigns global variables
C <- 1e6
p <- c()

# Prepares an empty dta.frame for the `for loop` to populate with the calculations
stocks <- data.frame("FTV" = double(0),
                     "ZBH" = double(0),
                     "ORCL" = double(0),
                     "CTXS" = double(0),
                     "XLNX" = double(0),
                     "ExpReturn" = double(0),
                     "Risk" = double(0)
)
```

```{r loop, echo=TRUE, warning=FALSE}

for (i in 1:3){
        # updates vector p
        p <- append(p,1) 
        #generates combinations (by3, by2, single)
        comb <- combn(1:ncol(stocks_considered), i)
        temp <- split(comb, rep(1:ncol(comb), each = nrow(comb)))
        
        # creates empty matrix for all combinations of stocks 
        summary <- matrix(nrow = ncol(comb), ncol = (ncol(stocks_considered)+2))
        colnames(summary) = c(stocks_names,"ExpReturn","Risk")
        
        # iterates for all combinations of stocks in each combination option
        for (j in 1:ncol(comb)) {
                # creates matrix based on the combinations in 'temp'
                x <- stocks_considered[,temp[[j]]] 
                # defines sigma and mu values
                sigma <- cov(x)
                mu <-sapply(x, mean)
                # Computes weight
                weight_calc <- (solve(sigma)%*%p)  / 
                        (as.numeric(t(p) %*% solve(sigma) %*% p))
                # Computes return
                return_calc <- t(weight_calc) %*% mu * C
                # Computes risk
                risk_calc <- t(weight_calc) %*% sigma %*% weight_calc * (C^2)
                
                # assigns the calculated weights to the respective columns
                summary[j,temp[[j]]] = c(t(weight_calc))
                # assigns the calculates returns and risks to the respective columns
                summary[j,6:7] = c(return_calc,risk_calc)
        }
        
        # replaces NA values with 0 
        summary <- replace_na(summary,0)
        # adds current 'summary' to the 'stocks' data.frame
        stocks <- rbind(stocks, summary)
}

```

\

<div style="text-align: justify">

 Finally, `stocks` matrix shows the combined portfolios with stock sizes of 3, 2, and 1 having a total of 25 portfolios with its weight of stocks, expected return as well as risk is provided.

</div>

```{r binding_calculations, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}
stocks <- cbind(as.data.frame(seq(1:25)),stocks)
colnames(stocks) = c("Portfolio", "FTV", "ZBH", "ORCL", "CTXS", "XLNX", "ExpReturn", "Risk")

kable(stocks, caption = "Calculated Weights for each stock in the Client's Portfolio options.")
```

<div style="text-align: justify">

Per your request, we can then find the portfolio that provides the least risk, and out of curiosity, the portfolio with the maximum return:

</div>

```{r RiskReturn, echo=TRUE, warning=FALSE}
# choose the portfolio with minimum risk
min_risk <- which.min(stocks$Risk)

# choose the portfolio with maximum return
max_return <- which.max(stocks$ExpReturn)

best <- stocks[min_risk,]
```

```{r MinMax, echo=FALSE, eval=TRUE}

MinMax <- data.frame(min_risk, max_return)
colnames(MinMax) = c("Portfolio with Lowest Risk", "Portfolio with Highest Return")
kable(MinMax)

```

<div style="text-align: justify">

The plot below gives a better visualization of the data, and one can also refer to the Appendix section for a detailed table with the weight, calculated Risk and Expected Return values. The red dot represents the best portfolio out of the 25 options generated, considering the constraints of the client. This portfolio presents a risk of `r  paste(format(round(best$Risk/ 1e6, 1), trim = TRUE), "millions")` and daily expected return of `r round(best$ExpReturn,2)`. The weight for each stock is `r round(best$FTV,2)` for *Fortive Corp. Stock*, `r round(best$ZBH,2)` for *Zimmer Biomet Holdings Inc. Stock*, and `r round(best$CTXS,2)` for *Citrix Systems Inc. Stock*.

</div>

```{r stock10, echo=FALSE, eval=TRUE, fig.align='center', fig.width=6.5, fig.height=4.5}

min_var <- stocks[which.min(stocks$Risk),]

p <- stocks %>%
ggplot(aes(x = Risk, y = ExpReturn)) +
        geom_point() +
        theme_classic() +
        labs(x = 'Risk',
             y = 'Returns',
             title = "Client's Optimized Portfolio Options") +
        geom_point(aes(x = Risk,
                       y = ExpReturn), data = min_var, color = 'red') +
        annotate(geom = 'segment', x = 0.14, xend = 0.135,  y = 0.01, 
                 yend = 0.06, color = 'red', arrow = arrow(type = "open")) +
        annotate(geom = 'segment', x = 0.22, xend = 0.2275,  y = 0.405, 
                 yend = 0.365, color = 'red', arrow = arrow(type = "open"))

ggplotly(p)

```


\
\

<div style="text-align: justify">

### Appendix

Table with all portfolio options, representing the weights for each company stock and respective Expected Return and Risks. The portfolio option with the lowest risk is highlighted in green, and the option with the highest return, in grey.

</div>

```{r stocks_table, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE}

library(kableExtra)

stocks$col = "Option Analyzed"
stocks$col[min_risk] = "Lowest Risk"
stocks$col[max_return] = "Highest Return"

colnames(stocks) = c("Portfolio", "FTV", "ZBH", "ORCL", "CTXS", "XLNX", "Expected Return", "Risk", "Status")

stocks %>%
  kable(booktabs = T) %>%
  kable_styling() %>%
  row_spec(which(stocks$Status == "Lowest Risk"),
           color = "black", background = "green") %>%
  row_spec(which(stocks$Status == "Highest Return"),
           color = "black", background = "grey")

```


