---
output: html_document
pagetitle: "Homework 2, Group 9: to the Boss"
---

 ```{css, echo=FALSE}
     .disclosure{
     text-align: justify;
     margin-left: auto;
     margin-right: auto;
     font-style: italic;
     width: 80%;
     }

```


## Dear Boss,
### Please find our finalized report below.
\

#### Best regards,
##### Ana Gabriela Itokazu, Jianfeng Zhang, and Takhellambam Bijoychandra Singh.


***
<div class="disclosure">

Portfolio developed for a homework activity during the class STAT 6210 - R Programming for Data Science (Auburn University, Fall 2020). The general idea is that the group works as a quantitative analysts for an investment bank, and we needed to present a Portfolio for our boss (Dr. Molinari, in this very real case) with the a client's options. This document was finalized in `r format(Sys.Date(), '%B %d, %Y')`. One can find more about this assignment [here](https://github.com/AU-R-Programming/HW2-9/blob/master/ToTheBoss.Rmd).

</div>


<div style="text-align: justify">

***
# Financial Report


# Required Library.

First of required libraries i.e. rvest, quantmod and tidyverse are called. 
```{r stock, echo=FALSE, include=FALSE}
library(rvest)
library(quantmod)
library(tidyverse)
```

# Stock selection.



```{r stock1, echo=FALSE}
url <- "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"
SP500 <- url %>%
  xml2::read_html() %>%
  html_nodes(xpath='//*[@id="mw-content-text"]/div/table[1]') %>%
  html_table()
SP500 <- SP500[[1]]
Tix <- SP500$Symbol
#randomly select 5 stocks
set.seed(100)
s=sample(Tix, 5)
```
Five stocks were selected randomly that download from this [link](https://en.wikipedia.org/wiki/List_of_S%26P_500_companies) i.e. `r s` where 

`r s[1]`=fORTIVE Corp, `r s[2]`= Zimmer Biomet Holdings, `r s[3]`=Oracle Corp., `r s[4]`=Citrix Systems, and `r s[5]`=Xilinx.

# Temporal Scale 

In this analysis, a  time span for last 3 years i.e. from  "2017-04-01" till "2020-04-01" were considered.
```{r stock2, echo=FALSE, include=FALSE}
#time span for last 3 years
three_year_ago <- seq(as.Date("2020-04-01"), length = 2, by = "-3 year")[2]
getSymbols(s, from = three_year_ago, to = as.Date("2020-04-01"))
```



# Compute returns

clcl() function is used to compute change in closing price.For example, "AAPL" company has change in closing price( clcl) as given below clcl= ((AAPL.Close at t+1 )-(AAPL.Close t))/(AAPL.Close at  t), where t= time step

```{r stock3, echo=FALSE}

FTV<- na.omit(ClCl(get(s[1])))
ZBH <- na.omit(ClCl(get(s[2])))
ORCL<- na.omit(ClCl(get(s[3])))
CTXS <- na.omit(ClCl(get(s[4])))
XLNX<- na.omit(ClCl(get(s[5])))
```

# Matrix 

A matrix with 10x7 dimensions is created to store the output of weight, expected daily return and risk for each portfolios.As it considers 3 portfolio out of 5 giving a combination of C(5,3)=10 portfolios.
```{r stock4, echo=FALSE}
final=matrix(NA,10, 7)
colnames(final)=c(s,"Exp return","Risk")
```


```{r stock5, echo=FALSE}
for (i in 1:10) {
  # attributes the returns data to a new object
  stocks=cbind(FTV,ZBH,ORCL,CTXS,XLNX)
  #compute the combination of picking 3 stocks out of 5 eqXLNXs to 10
  mat <- combn(1:5, 3)
  #converts to a list  with each element consist of 3 stocks
  aa=split(mat, rep(1:ncol(mat), each = nrow(mat)))
  #select 3 stocks from the object stocks having 5 stocks
  x=stocks[,aa[[i]]] 
  # Estimation of mu and Sigma
  sigma_stocks <- cov(x)
  colnames(sigma_stocks)=c("Stock1","Stock2","Stock3")
  mu <-sapply(x, mean)
  # Compute weight
  p<-c(1,1,1)
  num <-solve(sigma_stocks)%*%p
  den=t(p) %*% solve(sigma_stocks)%*%p
  omega_star <-1/den[1] * num
  # C= total amount of investment i.e. 1 million
  C=1e6
  #computes the expected daily returns
  mu_star <-t(omega_star)%*% mu*C
  # computes the daily risk 
  sigma_star=t(omega_star)%*%sigma_stocks%*%omega_star*C^2
  #Insert the expected daily return to the predefined matrix
  final[i,aa[[i]]]=c(t(omega_star))
   #Insert the daily risk to the predefined matrix
  final[i,6:7]=c(mu_star,sigma_star)
}
#replace all NA value with 0
# this is the final output showing weight, daily return and risk for considering 3 stocks out of 5.
stock3=replace_na(final,0)
```

Likewise, second matrix having 10x7 dimension is created for storing the weight, expected daily return and risk of each portfolios of C(5,2)=10.This is done as in the previous matrix.

```{r stock6, echo=FALSE}
# Selecting stock2
final1=matrix(NA,10, 7)
colnames(final)=c(s,"Exp return","Risk")
for (i in 1:10) {
  stocks=cbind(FTV,ZBH,ORCL,CTXS,XLNX)
  mat <- combn(1:5, 2)
  aa=split(mat, rep(1:ncol(mat), each = nrow(mat)))
  x=stocks[,aa[[i]]] 
  sigma_stocks <- cov(x)
  colnames(sigma_stocks)=c("Stock1","Stock2")
  mu <-sapply(x, mean)
  p<-c(1,1)
  num <-solve(sigma_stocks)%*%p
  den=t(p) %*% solve(sigma_stocks)%*%p
  omega_star <-1/den[1] * num
  C=1e6
  mu_star <-t(omega_star)%*% mu*C
  sigma_star=t(omega_star)%*%sigma_stocks%*%omega_star*C^2
  final1[i,aa[[i]]]=c(t(omega_star))
  final1[i,6:7]=c(mu_star,sigma_star)
}
stock2=replace_na(final1,0)
```

Again, matrix with 5x1 dimensions is created for storing weight, the daily expected return and risk considering 1 stocks out of 5 giving a combination of C(5,1)=5 is available. The procedure is again same as done above code.

```{r stock7, echo=FALSE}
final2=matrix(NA,5, 7)
colnames(final)=c(s,"Exp return","Risk")
for (i in 1:5) {
  stocks=cbind(FTV,ZBH,ORCL,CTXS,XLNX)
  mat <- combn(1:5, 1)
  aa=split(mat, rep(1:ncol(mat), each = nrow(mat)))
  x=stocks[,aa[[i]]] 
  sigma_stocks <- cov(x)
  mu <-sapply(x, mean)
  p<-c(1)
  num <-solve(sigma_stocks)%*%p
  den=t(p) %*% solve(sigma_stocks)%*%p
  omega_star <-1/den[1] * num
  C=1e6
  mu_star <-t(omega_star)%*% mu*C
  sigma_star=t(omega_star)%*%sigma_stocks%*%omega_star*C^2
  final2[i,aa[[i]]]=c(t(omega_star))
  final2[i,6:7]=c(mu_star,sigma_star)
}
stock1=replace_na(final2,0)
```
 
 Finally, *stock* matrix showed the combine portfolios showing  with using stock size of 3,2 and 1 having a total of 25 portfolios.

```{r stock8, echo=FALSE}
#combing all portfolios
stock=rbind(stock3,stock2,stock1)
round(stock,3)
```

The best portfolios with its weight of stocks, daily expected return as well as risk is provided.
```{r stock9, echo=FALSE}
#choose the row showing minimum risk
min_risk=which.min(stock[,7])
# rounding the values upto 3 decimals
best=round(stock[min_risk,],3)
best
```

Graphically, it is shown in the plot below. The red dotted showed best portfolio out of the 25 portfolios shown in black having minimum risk of `r best[7]` and daily expected return of `r best[6]`. The weight for each stocks of *FTV*, *ZBH*, and *CTXS* are `r best[1]`,`r best[2]`, and `r best[4]` respectively. So, the portfolio 2 is the best option one can invest considering the minimum risk.
```{r stock10, echo=TRUE}
#plot of all portfolios
plot(stock[-min_risk,7],stock[-min_risk,6],pch=1,type = "p",  col = 1, 
     xlab = "Investment Daily Risk",
     ylab = "Investment Daily Expected Return", main="Stock Portfolios")
#addition of portfolio having smallest variance
points(best[7], best[6],pch = 1, col = 10, type = "p")
#add legends
legend(5.8e8,1500, c("Possible portfolio", "Min-Variance Portfolio"), col = c(1,10),
       lty = c(-2, -1), pch = c(1, 1))

```


